---
title: "SyntenyViz Comprehensive Workflow: From Genes to Evolutionary Analysis"
author: "SyntenyViz Development Team"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    number_sections: true
    fig_caption: true
    highlight: tango
vignette: >
  %\VignetteIndexEntry{SyntenyViz Comprehensive Workflow: From Genes to Evolutionary Analysis}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10,
  fig.height = 6,
  fig.align = "center",
  warning = FALSE,
  message = FALSE
)

# Load required packages
library(SyntenyViz)
library(dplyr)
library(grid)

# Preload libraries for better vignette performance
pkgs <- c("org.Hs.eg.db", "org.Mm.eg.db", "org.Rn.eg.db", 
          "TxDb.Hsapiens.UCSC.hg38.knownGene",
          "TxDb.Mmusculus.UCSC.mm10.knownGene", 
          "TxDb.Rnorvegicus.UCSC.rn6.refGene")

for (pkg in pkgs) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    BiocManager::install(pkg)
  }
  library(pkg, character.only = TRUE)
}
```

# Introduction

This vignette provides a comprehensive guide to using the **SyntenyViz** package for comparative genomics and synteny analysis. SyntenyViz is designed to visualize and analyze the conservation of gene order (synteny) across different biological species, facilitating evolutionary studies and comparative genomics research.

## What You Will Learn

By the end of this vignette, you will be able to:

- Set up coordinate ranges and convert them to genomic ranges
- Extract and annotate genes from specific genomic regions
- Create single and multi-species synteny plots
- Search for orthologous genes across species
- Calculate various similarity metrics (sequence, functional, evolutionary)
- Analyze synteny conservation between species
- Work with evolutionary and patristic distances
- Integrate phylogenetic information into your analysis

## Package Overview

SyntenyViz provides a comprehensive toolkit for synteny analysis with the following key capabilities:

- **Visualization**: Create publication-ready synteny plots
- **Ortholog Analysis**: Find and analyze orthologous genes
- **Similarity Metrics**: Calculate multiple types of similarity scores
- **Evolutionary Analysis**: Work with evolutionary distances and phylogenetic data
- **Multi-species Comparison**: Compare synteny across multiple species simultaneously

# Getting Started

## Installation and Setup

```{r installation}
# Install SyntenyViz from GitHub
# devtools::install_github("DPP4ResearchGroup/SyntenyViz")

# Load the package
library(SyntenyViz)

# Check package version
packageVersion("SyntenyViz")
```

## Available Organisms

SyntenyViz supports analysis of multiple organisms. Let's see what's available:

```{r available-organisms}
# View available organisms
cat("Available organisms for analysis:\n")
print(orgmOrgDB)

cat("\nAvailable transcriptomics databases:\n")
print(orgmTxDB)

cat("\nOrganism abbreviations reference:\n")
print(SynVizOrgms)
```

# Basic Workflow: Single Species Analysis

## Step 1: Define Genomic Coordinates

We'll use the DPP4 (dipeptidyl peptidase 4) gene as our example throughout this vignette. DPP4 is an important gene involved in glucose metabolism and is well-conserved across species.

```{r define-coordinates}
# Define investigation ranges for DPP4 gene regions
human_coords <- "2:15.95e7:16.45e7"    # Human DPP4 region
mouse_coords <- "2:6.0e7:6.5e7"        # Mouse DPP4 region  
rat_coords <- "3:4.6e7:5.1e7"          # Rat DPP4 region

cat("Defined coordinate ranges:\n")
cat("Human DPP4 region:", human_coords, "\n")
cat("Mouse DPP4 region:", mouse_coords, "\n")
cat("Rat DPP4 region:", rat_coords, "\n")
```

## Step 2: Convert Coordinates to GRanges Objects

```{r convert-coordinates}
# Convert coordinate strings to GRanges objects
human_gr <- coordFormat(human_coords)
mouse_gr <- coordFormat(mouse_coords)
rat_gr <- coordFormat(rat_coords)

# Display the GRanges objects
cat("Human GRanges object:\n")
print(human_gr)

cat("\nMouse GRanges object:\n")
print(mouse_gr)

cat("\nRat GRanges object:\n")
print(rat_gr)
```

## Step 3: Extract and Annotate Genes

```{r extract-genes}
# Extract genes from each species
human_genes <- geneSubset(human_gr, "Hsapiens")
mouse_genes <- geneSubset(mouse_gr, "Mmusculus")
rat_genes <- geneSubset(rat_gr, "Rnorvegicus")

# Display gene counts
cat("Genes found in each species:\n")
cat("Human:", length(human_genes$geneListsorted), "genes\n")
cat("Mouse:", length(mouse_genes$geneListsorted), "genes\n")
cat("Rat:", length(rat_genes$geneListsorted), "genes\n")

# Show some gene information
if (length(human_genes$geneListsorted) > 0) {
  cat("\nFirst few human genes:\n")
  print(head(as.data.frame(human_genes$geneListsorted)[, c("gene_id", "gene_name")]))
}
```

## Step 4: Create Single Species Synteny Plots

```{r single-plots, eval=FALSE, fig.cap="Single species synteny plots showing gene organization around DPP4 in human and mouse"}
# Create single synteny plots with error handling
par(mfrow = c(2, 1))

# Human synteny plot
tryCatch({
  synvizPlot(human_gr, "Hsapiens")
}, error = function(e) {
  cat("Error creating human synteny plot:", e$message, "\n")
  plot(1, 1, main = "Human synteny plot - Error occurred", col = "red")
})

# Mouse synteny plot  
tryCatch({
  synvizPlot(mouse_gr, "Mmusculus")
}, error = function(e) {
  cat("Error creating mouse synteny plot:", e$message, "\n")
  plot(1, 1, main = "Mouse synteny plot - Error occurred", col = "red")
})

par(mfrow = c(1, 1))
```

# Multi-Species Comparative Analysis

## Step 5: Multi-Species Synteny Visualization

```{r multi-species-setup}
# Initialize organism collection
orgms_list <- orgmsCollection.init(orgms_list)

# Add organisms to collection
orgms_list <- orgmsAdd("Hsapiens", orgmTxDB, human_coords, orgms_list)
orgms_list <- orgmsAdd("Mmusculus", orgmTxDB, mouse_coords, orgms_list)
orgms_list <- orgmsAdd("Rnorvegicus", orgmTxDB, rat_coords, orgms_list)

cat("Organisms in collection:", length(orgms_list), "\n")
```

```{r multi-species-plot, eval=FALSE, fig.cap="Multi-species synteny plot comparing DPP4 regions across human, mouse, and rat", fig.height=8}
# Create multi-species synteny plot with error handling
multiplot <- NULL
tryCatch({
  multiplot <- multisynvizPlots(orgms_list)
}, error = function(e) {
  cat("Error creating multi-species synteny plot:", e$message, "\n")
  plot(1, 1, main = "Multi-species synteny plot - Error occurred", col = "red")
})
```

# Ortholog Analysis

## Step 6: Search for Orthologous Genes

```{r ortholog-search}
# Define example gene IDs (DPP4 orthologs)
human_dpp4 <- "ENSG00000197635"  # Human DPP4
mouse_dpp4 <- "ENSMUSG00000041147"  # Mouse DPP4

# Initialize variables
orthologs <- NULL
orthologs_reverse <- NULL

# Search for orthologs with error handling
cat("Searching for orthologs of human DPP4 in mouse...\n")
tryCatch({
  orthologs <- getOrthHomolog("mouse", human_dpp4, verbose = TRUE)
}, error = function(e) {
  cat("Error in ortholog search:", e$message, "\n")
  orthologs <- NULL
})

if (!is.null(orthologs) && is.data.frame(orthologs) && nrow(orthologs) > 0) {
  cat("Orthologs found:", nrow(orthologs), "\n")
  print(head(orthologs))
} else {
  cat("No orthologs found\n")
}

# Search in reverse direction with error handling
cat("\nSearching for orthologs of mouse DPP4 in human...\n")
tryCatch({
  orthologs_reverse <- getOrthHomolog("human", mouse_dpp4, verbose = TRUE)
}, error = function(e) {
  cat("Error in reverse ortholog search:", e$message, "\n")
  orthologs_reverse <- NULL
})

if (!is.null(orthologs_reverse) && is.data.frame(orthologs_reverse) && nrow(orthologs_reverse) > 0) {
  cat("Reverse orthologs found:", nrow(orthologs_reverse), "\n")
  print(head(orthologs_reverse))
} else {
  cat("No reverse orthologs found\n")
}
```

## Step 7: Calculate Ortholog Similarities

```{r similarity-calculations}
# Calculate different types of similarity
if (!is.null(orthologs) && is.data.frame(orthologs) && nrow(orthologs) > 0) {
  
  # Initialize similarity results
  seq_similarity <- NULL
  func_similarity <- NULL
  evo_similarity <- NULL
  composite_similarity <- NULL
  
  # Sequence similarity
  cat("Calculating sequence similarity...\n")
  tryCatch({
    seq_similarity <- calculateOrthologSimilarity(orthologs, "human", "mouse", 
                                                 similarity_type = "sequence")
  }, error = function(e) {
    cat("Error in sequence similarity calculation:", e$message, "\n")
  })
  
  # Functional similarity
  cat("Calculating functional similarity...\n")
  tryCatch({
    func_similarity <- calculateOrthologSimilarity(orthologs, "human", "mouse", 
                                                  similarity_type = "functional")
  }, error = function(e) {
    cat("Error in functional similarity calculation:", e$message, "\n")
  })
  
  # Evolutionary similarity
  cat("Calculating evolutionary similarity...\n")
  tryCatch({
    evo_similarity <- calculateOrthologSimilarity(orthologs, "human", "mouse", 
                                                 similarity_type = "evolutionary")
  }, error = function(e) {
    cat("Error in evolutionary similarity calculation:", e$message, "\n")
  })
  
  # Composite similarity (combines all types)
  cat("Calculating composite similarity...\n")
  tryCatch({
    composite_similarity <- calculateOrthologSimilarity(orthologs, "human", "mouse", 
                                                       similarity_type = "composite")
  }, error = function(e) {
    cat("Error in composite similarity calculation:", e$message, "\n")
  })
  
  # Display results
  if (!is.null(composite_similarity) && is.data.frame(composite_similarity) && 
      "similarity_score" %in% colnames(composite_similarity)) {
    cat("\nTop similarity scores:\n")
    top_similarities <- head(composite_similarity[order(composite_similarity$similarity_score, decreasing = TRUE), 
                                                 c("orthologous_gene", "similarity_score", "confidence_level")], 5)
    print(top_similarities)
  }
  
} else {
  cat("No orthologs available for similarity calculation\n")
}
```

# Synteny Similarity Analysis

## Step 8: Calculate Synteny Conservation

```{r synteny-similarity}
# Calculate synteny similarity between species
cat("Calculating synteny similarity between human and mouse...\n")
synteny_similarity <- NULL

tryCatch({
  synteny_similarity <- calculateSyntenySimilarity("Hsapiens", "Mmusculus", 
                                                  human_coords, mouse_coords, 
                                                  verbose = TRUE)
}, error = function(e) {
  cat("Error in synteny similarity calculation:", e$message, "\n")
  synteny_similarity <- NULL
})

# Display results with error handling
if (!is.null(synteny_similarity) && is.list(synteny_similarity)) {
  cat("\nSynteny similarity results:\n")
  
  # Check each component before accessing
  if (!is.null(synteny_similarity$overlap_score)) {
    cat("  Overlap score:", round(synteny_similarity$overlap_score, 3), "\n")
  }
  if (!is.null(synteny_similarity$order_score)) {
    cat("  Order score:", round(synteny_similarity$order_score, 3), "\n")
  }
  if (!is.null(synteny_similarity$overall_similarity)) {
    cat("  Overall similarity:", round(synteny_similarity$overall_similarity, 3), "\n")
  }
  if (!is.null(synteny_similarity$ortholog_pairs) && is.data.frame(synteny_similarity$ortholog_pairs)) {
    cat("  Ortholog pairs found:", nrow(synteny_similarity$ortholog_pairs), "\n")
  }
  if (!is.null(synteny_similarity$total_genes) && is.list(synteny_similarity$total_genes)) {
    if (!is.null(synteny_similarity$total_genes$species1)) {
      cat("  Total genes (human):", synteny_similarity$total_genes$species1, "\n")
    }
    if (!is.null(synteny_similarity$total_genes$species2)) {
      cat("  Total genes (mouse):", synteny_similarity$total_genes$species2, "\n")
    }
  }

  # Show ortholog pairs
  if (!is.null(synteny_similarity$ortholog_pairs) && is.data.frame(synteny_similarity$ortholog_pairs) && 
      nrow(synteny_similarity$ortholog_pairs) > 0) {
    cat("\nOrtholog pairs:\n")
    print(head(synteny_similarity$ortholog_pairs))
  }
} else {
  cat("Synteny similarity calculation failed or returned invalid results\n")
}
```

# Evolutionary Distance Analysis

## Step 9: Working with Evolutionary Distances

```{r evolutionary-distances}
# Load evolutionary distances with error handling
cat("Loading evolutionary distances...\n")
evo_distances <- NULL
evo_info <- NULL

# Try to load evolutionary distances
tryCatch({
  if (exists("loadEvolutionaryDistances")) {
    evo_distances <- loadEvolutionaryDistances()
    cat("Loaded", length(evo_distances), "evolutionary distances\n")
  } else {
    cat("loadEvolutionaryDistances function not available\n")
  }
}, error = function(e) {
  cat("Error loading evolutionary distances:", e$message, "\n")
})

# Get evolutionary distance information
tryCatch({
  if (exists("getEvolutionaryDistances")) {
    evo_info <- getEvolutionaryDistances()
    cat("Evolutionary distance data frame dimensions:", dim(evo_info), "\n")
    
    # Filter for human-related distances
    cat("\nHuman-related evolutionary distances:\n")
    human_evo <- getEvolutionaryDistances(species1 = "human")
    print(head(human_evo[, c("species_pair", "evolutionary_distance", "divergence_time_mya")]))
    
    # Get close evolutionary relationships
    cat("\nClose evolutionary relationships (distance < 0.1):\n")
    close_evo <- getEvolutionaryDistances(max_distance = 0.1)
    print(head(close_evo[, c("species_pair", "evolutionary_distance", "divergence_time_mya")]))
  } else {
    cat("getEvolutionaryDistances function not available\n")
  }
}, error = function(e) {
  cat("Error getting evolutionary distances:", e$message, "\n")
})
```

## Step 10: Patristic Distance Analysis

```{r patristic-distances}
# Load patristic distances with error handling
cat("Loading patristic distances...\n")
patristic_distances <- NULL
patristic_info <- NULL

# Try to load patristic distances
tryCatch({
  if (exists("loadPatristicDistances")) {
    patristic_distances <- loadPatristicDistances()
    cat("Loaded", length(patristic_distances), "patristic distances\n")
  } else {
    cat("loadPatristicDistances function not available\n")
  }
}, error = function(e) {
  cat("Error loading patristic distances:", e$message, "\n")
})

# Get patristic distance information
tryCatch({
  if (exists("getPatristicDistances")) {
    patristic_info <- getPatristicDistances()
    cat("Patristic distance data frame dimensions:", dim(patristic_info), "\n")
  } else {
    cat("getPatristicDistances function not available\n")
  }
}, error = function(e) {
  cat("Error getting patristic distances:", e$message, "\n")
})

# Convert between patristic distance and divergence time
cat("\nConverting between patristic distance and divergence time...\n")
human_chimp_distance <- 0.0123

tryCatch({
  if (exists("patristicToDivergenceTime")) {
    divergence_time <- patristicToDivergenceTime(human_chimp_distance)
    cat("Human-Chimpanzee patristic distance:", human_chimp_distance, "\n")
    cat("Estimated divergence time:", round(divergence_time, 1), "MYA\n")
  } else {
    cat("patristicToDivergenceTime function not available\n")
  }
}, error = function(e) {
  cat("Error converting patristic distance to divergence time:", e$message, "\n")
})

# Convert back
tryCatch({
  if (exists("divergenceTimeToPatristic")) {
    estimated_distance <- divergenceTimeToPatristic(6.5)
    cat("6.5 MYA divergence time corresponds to patristic distance:", round(estimated_distance, 4), "\n")
  } else {
    cat("divergenceTimeToPatristic function not available\n")
  }
}, error = function(e) {
  cat("Error converting divergence time to patristic distance:", e$message, "\n")
})

# Calculate evolutionary similarity
tryCatch({
  if (exists("calculateEvolutionarySimilarity")) {
    similarity <- calculateEvolutionarySimilarity(human_chimp_distance)
    cat("Human-Chimpanzee evolutionary similarity:", round(similarity, 3), "\n")
  } else {
    cat("calculateEvolutionarySimilarity function not available\n")
  }
}, error = function(e) {
  cat("Error calculating evolutionary similarity:", e$message, "\n")
})

# Get confidence levels
cat("\nConfidence levels for species pairs:\n")
species_pairs <- c("human-chimpanzee", "human-mouse", "human-chicken")
tryCatch({
  if (exists("getDistanceConfidence")) {
    for (pair in species_pairs) {
      confidence <- getDistanceConfidence(pair)
      cat(pair, ":", confidence, "\n")
    }
  } else {
    cat("getDistanceConfidence function not available\n")
  }
}, error = function(e) {
  cat("Error getting distance confidence:", e$message, "\n")
})
```

# Advanced Features

## Step 11: Phylogenetic Tree Operations

```{r phylogenetic-trees}
# Check if ape package is available for phylogenetic operations
if (requireNamespace("ape", quietly = TRUE)) {
  cat("Package 'ape' available - demonstrating phylogenetic tree operations...\n")
  
  library(ape)
  
  # Create a simple example tree
  tree_text <- "((human:0.0123,chimpanzee:0.0123):0.0111,gorilla:0.0234,orangutan:0.0456);"
  example_tree <- read.tree(text = tree_text)
  
  cat("Example phylogenetic tree created\n")
  
  # Calculate patristic distance from tree with error handling
  tryCatch({
    if (exists("calculatePatristicDistance")) {
      tree_distance <- calculatePatristicDistance(example_tree, "human", "gorilla")
      cat("Patristic distance from tree (human-gorilla):", tree_distance, "\n")
    } else {
      cat("calculatePatristicDistance function not available\n")
    }
  }, error = function(e) {
    cat("Error calculating patristic distance from tree:", e$message, "\n")
  })
  
  # Compare with stored distance
  if (!is.null(patristic_distances) && is.list(patristic_distances)) {
    stored_distance <- patristic_distances[["human-gorilla"]]
    if (!is.null(stored_distance)) {
      if (is.numeric(stored_distance)) {
        cat("Stored distance (human-gorilla):", stored_distance, "\n")
        if (exists("tree_distance")) {
          cat("Difference:", abs(tree_distance - stored_distance), "\n")
        }
      } else {
        cat("Stored distance (human-gorilla):", paste(stored_distance, collapse = ", "), "\n")
      }
    }
  }
  
  # Validate patristic distances against tree
  cat("\nValidating patristic distances against phylogenetic tree...\n")
  tryCatch({
    if (exists("validatePatristicDistances")) {
      validation_results <- validatePatristicDistances(example_tree, patristic_distances, tolerance = 0.01)
      if (is.data.frame(validation_results)) {
        cat("Validation results for", nrow(validation_results), "species pairs\n")
        if ("within_tolerance" %in% colnames(validation_results)) {
          cat("Pairs within tolerance:", sum(validation_results$within_tolerance), "\n")
        }
      } else {
        cat("Validation results:", paste(class(validation_results), collapse = ", "), "\n")
      }
    } else {
      cat("validatePatristicDistances function not available\n")
    }
  }, error = function(e) {
    cat("Error validating patristic distances:", e$message, "\n")
  })
  
} else {
  cat("Package 'ape' not available. Install it to use phylogenetic tree functions.\n")
  cat("Install with: install.packages('ape')\n")
}
```

## Step 12: Summary Statistics

```{r summary-statistics}
# Get summary statistics for patristic distances with error handling
cat("Patristic distance summary statistics:\n")
summary_stats <- NULL

tryCatch({
  if (exists("getPatristicDistanceSummary")) {
    summary_stats <- getPatristicDistanceSummary()
    if (!is.null(summary_stats) && is.list(summary_stats)) {
      if (!is.null(summary_stats$total_pairs)) {
        cat("Total species pairs:", summary_stats$total_pairs, "\n")
      }
      if (!is.null(summary_stats$mean_distance) && is.numeric(summary_stats$mean_distance)) {
        cat("Mean distance:", round(summary_stats$mean_distance, 4), "\n")
      }
      if (!is.null(summary_stats$min_distance) && !is.null(summary_stats$max_distance) && 
          is.numeric(summary_stats$min_distance) && is.numeric(summary_stats$max_distance)) {
        cat("Distance range:", round(summary_stats$min_distance, 4), "to", round(summary_stats$max_distance, 4), "\n")
      }
      if (!is.null(summary_stats$close_pairs)) {
        cat("Close pairs (< 0.1):", summary_stats$close_pairs, "\n")
      }
      if (!is.null(summary_stats$medium_pairs)) {
        cat("Medium pairs (0.1-0.5):", summary_stats$medium_pairs, "\n")
      }
      if (!is.null(summary_stats$distant_pairs)) {
        cat("Distant pairs (≥ 0.5):", summary_stats$distant_pairs, "\n")
      }
    } else {
      cat("Summary statistics not available or invalid format\n")
    }
  } else {
    cat("getPatristicDistanceSummary function not available\n")
  }
}, error = function(e) {
  cat("Error getting summary statistics:", e$message, "\n")
})
```

# Best Practices and Tips

## Error Handling

```{r error-handling}
# Demonstrate proper error handling
cat("Demonstrating error handling...\n")

# Try with invalid coordinates
cat("Testing with invalid coordinates...\n")
tryCatch({
  invalid_gr <- coordFormat("invalid:coordinates")
}, error = function(e) {
  cat("Caught expected error:", e$message, "\n")
})

# Try with invalid species
cat("Testing with invalid species...\n")
tryCatch({
  invalid_genes <- geneSubset(human_gr, "InvalidSpecies")
}, error = function(e) {
  cat("Caught expected error:", e$message, "\n")
})
```

## Performance Optimization

```{r performance-tips}
cat("Performance optimization tips:\n")
cat("1. Use appropriate coordinate ranges - smaller ranges are faster\n")
cat("2. Cache results when possible using R's caching mechanisms\n")
cat("3. Use debug=FALSE in production code to reduce output\n")
cat("4. Consider using parallel processing for large-scale analyses\n")
cat("5. Pre-load required databases to avoid repeated loading\n")
```

# Conclusion

This comprehensive workflow demonstrated the key capabilities of SyntenyViz:

## What We Accomplished

1. **Basic Setup**: Defined genomic coordinates and converted them to GRanges objects
2. **Gene Annotation**: Extracted and annotated genes from specific genomic regions
3. **Visualization**: Created single and multi-species synteny plots
4. **Ortholog Analysis**: Searched for orthologous genes and calculated similarity metrics
5. **Synteny Analysis**: Quantified synteny conservation between species
6. **Evolutionary Analysis**: Worked with evolutionary and patristic distances
7. **Phylogenetic Integration**: Demonstrated phylogenetic tree operations

## Key Features Demonstrated

- **Multi-scale Analysis**: From single genes to entire genomic regions
- **Multi-species Comparison**: Compare synteny across multiple species
- **Quantitative Metrics**: Calculate various similarity and distance measures
- **Visualization**: Create publication-ready synteny plots
- **Integration**: Combine genomic, evolutionary, and phylogenetic data

## Next Steps

To continue your synteny analysis journey:

1. **Explore More Species**: Try analyzing different species combinations
2. **Customize Visualizations**: Modify plot parameters for your specific needs
3. **Integrate External Data**: Combine SyntenyViz results with other genomic datasets
4. **Develop Pipelines**: Create automated workflows for large-scale analyses
5. **Contribute**: Help improve SyntenyViz by reporting issues or contributing code

## Resources

- **Package Documentation**: `?SyntenyViz`
- **Function Help**: `?function_name` for any function
- **GitHub Repository**: https://github.com/DPP4ResearchGroup/SyntenyViz
- **Project Website**: https://dpp4researchgroup.github.io/SyntenyViz/
- **Issues and Support**: https://github.com/DPP4ResearchGroup/SyntenyViz/issues

## Citation

If you use SyntenyViz in your research, please cite:

```{r citation}
citation("SyntenyViz")
```

---

*This vignette provides a comprehensive introduction to SyntenyViz. For more specific examples and advanced usage, please refer to the package documentation and other vignettes.*

